Continous time Markov chain models; \\ extension, simulation and visualisation

### 2014-10-23 chapters/chapter01.tex
some comments and labels

%PL: Since you list the mutations for the right branch, you may as well list the one on the left branch as well
% FB: not sure what you mean, should I add some annotation on that branch?
\begin{figure}[H]
\centering
\begingroup
\everymath{\displaystyle}
{\Large
\begin{displaymath} % 
\xymatrix{
& \color{gray2}A \ar[dl] \ar[drdr]^{ \color{gray2}\begin{array}{c}
A\rightarrow G\\
G\rightarrow C
\end{array}} & & \\
T & & & \\
& & & C \\
}
%     \xymatrix@R+1pc{ 
% \color{gray2}A \ar[r] & \color{gray2}T \ar[r] & A \\
% \color{gray2}A \ar[r] & \color{gray2}T \ar[r] & G \\
% \color{gray2}A  \ar[rr]_{ \color{gray2}\begin{array}{c}
% A\rightarrow G\\
% G\rightarrow C
% \end{array}} &&  C
%     } % 
\end{displaymath}
}% END: Large
\endgroup
\caption{
{ \footnotesize 
{\bf Evolution at a single site.} Over time characters at the site change, leading to the observed data (black). 
%Some of the mutations may be unobserved. %PL: All mutations are unobserved!!!!
Each site evolves independently.
The longer the evolutionary time, the higher the probability that multiple substitutions occur on the same site.
}% END: footnotesize
}
\label{fig:alignment}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.4]{poisson}
\caption{
{ \footnotesize 
{\bf Independent realizations of the Poisson process with intensity $r=1$.}
Waiting times between mutations are \emph{iid} exponentially distributed random variables with mean $1/r$.
} % END: footnotesize
}
\label{fig:poisson}
\end{figure}

>>>>

%PL: Since you list the mutations for the right branch, you may as well list the one on the left branch as well
% FB: not sure what you mean, should I add some annotation on that branch? I explicite left it empty, as the rught brancg is longer so it has more substitutions on it than the left one
\begin{figure}[H]
\centering
\begingroup
\everymath{\displaystyle}
{\Large
\begin{displaymath} % 
\xymatrix{
& \color{gray2}A \ar[dl] \ar[drdr]^{ \color{gray2}\begin{array}{c}
A\rightarrow G\\
G\rightarrow C
\end{array}} & & \\
T & & & \\
& & & C \\
}
%     \xymatrix@R+1pc{ 
% \color{gray2}A \ar[r] & \color{gray2}T \ar[r] & A \\
% \color{gray2}A \ar[r] & \color{gray2}T \ar[r] & G \\
% \color{gray2}A  \ar[rr]_{ \color{gray2}\begin{array}{c}
% A\rightarrow G\\
% G\rightarrow C
% \end{array}} &&  C
%     } % 
\end{displaymath}
}% END: Large
\endgroup
\caption{
{ \footnotesize 
{\bf Evolution at a single site.} Over time characters at the site change, leading to the observed data (black). 
%Some of the mutations may be unobserved. %PL: All mutations are unobserved!!!!
Each site evolves independently.
The longer the evolutionary time, the higher the probability that multiple substitutions occur on the same site.
}% END: footnotesize
}
\label{fig:alignment}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.4]{poisson}
\caption{
{ \footnotesize 
{\bf Three independent realizations of the Poisson process with intensity $r=1$.}
Waiting times between mutations are \emph{iid} exponentially distributed random variables with mean $1/r$.
} % END: footnotesize
}
\label{fig:poisson}
\end{figure}
